RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-09-16 validation.tex
last todo's

\begin{table*}[t]
\centering
\begin{tabularx}{0.95\textwidth}{l|l|l|l|l|l||l|l|l}
& very difficult & difficult & neutral & easy & very easy & avg (1-5) & std. dev. & p-value \\
\hline
Q1 & 2 (12.5\%) & 1 (6.3\%)  & 6 (37.5\%) & 6 (37.5\%) & 1 (6.3\%)  & 3.2 & 1.1 & 0.509 \\
Q2 & 2 (12.5\%) & 2 (12.5\%) & 4 (25.0\%) & 8 (50.0\%) & 0 (0.0\%)  & 3.1 & 1.1 & 0.652 \\
Q3 & 0 (0.0\%)  & 3 (20.0\%) & 4 (26.7\%) & 5 (33.3\%) & 3 (20.0\%) & 3.5 & 1.1 & 0.072 \\
Q4 & 2 (12.5\%) & 5 (31.3\%) & 6 (37.5\%) & 3 (18.8\%) & 0 (0.0\%)  & 2.6 & 1.0 & 0.138 
\end{tabularx}
\caption{Participant ratings and statistical results for the usability of the RationalGRL tool\todo{Floris}{Marc}{Fix table width}}
\label{table:survey:table1}
\end{table*}

@@

First, the participants had to perform the modeling task. They produced RationalGRL models containing on average 3 arguments (in addition  to goals, tasks, etc.) from the short transcript. Some of the examples of RationalGRL models the users created can be found in Appendix~\ref{sect:survey-screenshots}. The full results of the survey can be downloaded from \url{www.rationalgrl.com}, on the page ``Empirical study''. \todo{Floris}{Marc}{Staan de results op de webpagina?}

>>>>

\begin{table*}[t]
\centering
\begin{tabularx}{0.8\textwidth}{l|l|l|l|l|l||l|l|l}
& very difficult & difficult & neutral & easy & very easy & avg (1-5) & std. dev. & p-value \\
\hline
Q1 & 2 (12.5\%) & 1 (6.3\%)  & 6 (37.5\%) & 6 (37.5\%) & 1 (6.3\%)  & 3.2 & 1.1 & 0.509 \\
Q2 & 2 (12.5\%) & 2 (12.5\%) & 4 (25.0\%) & 8 (50.0\%) & 0 (0.0\%)  & 3.1 & 1.1 & 0.652 \\
Q3 & 0 (0.0\%)  & 3 (20.0\%) & 4 (26.7\%) & 5 (33.3\%) & 3 (20.0\%) & 3.5 & 1.1 & 0.072 \\
Q4 & 2 (12.5\%) & 5 (31.3\%) & 6 (37.5\%) & 3 (18.8\%) & 0 (0.0\%)  & 2.6 & 1.0 & 0.138 
\end{tabularx}
\caption{Participant ratings and statistical results for the usability of the RationalGRL tool}
\label{table:survey:table1}
\end{table*}

@@

First, the participants had to perform the modeling task. They produced RationalGRL models containing on average 3 arguments (in addition  to goals, tasks, etc.) from the short transcript. Some of the examples of RationalGRL models the users created can be found in Appendix~\ref{sect:survey-screenshots}.\footnote{The full results of the survey can be downloaded from \url{www.rationalgrl.com}, on the page ``Empirical study''.}
